**Socio-economic and geographic determinants of Covid-19 vaccination**

### 2023-04-23 manuscript_v4/03-results.qmd
need to fix modelplot figure

data_summary<-clean_data %>%
  tbl_summary(percent="row",
              by= first_dose,
              include=c(income_ord,
                        Age_group_ord,
                        Health_Region,
                        Month,
                        Race),
              label=list(Health_Region ~ "Health Region",
                 Age_group_ord ~ "Age Group",
                 income_ord="Income (CAD)")
  ) %>% bold_labels()

@@

t0<-m0 %>%
  tbl_regression(exponentiate = TRUE,
                 label=list(Health_Region ~ "Health Region",
                            Age_group_ord ~ "Age Group",
                            income_ord="Income (CAD)")) %>%
  bold_labels()

>>>>

data_summary<-clean_data %>%
  tbl_summary(percent="row",
              by= first_dose,
              include=c(income_ord,
                        Age_group_ord,
                        Health_Region,
                        Month,
                        Race),
              label=list(Health_Region ~ "Health Region",
                 Age_group_ord ~ "Age Group",
                 income_ord="Income (CAD)")
  ) %>% add_p("prop.test")%>%
  bold_labels()

@@

# t0<-m0 %>%
#   tbl_regression(exponentiate = TRUE,
#                  label=list(Health_Region ~ "Health Region",
#                             Age_group_ord ~ "Age Group",
#                             income_ord="Income (CAD)")) %>%
#   bold_labels()

modelplot(m0)+
  aes(color=ifelse(p.value<0.05, "Significant","Non-significant"))+
  scale_color_manual(values=c("black","red"))

modelplot(m2)+
  aes(color=ifelse(p.value<0.05, "Significant","Non-significant"))+
  scale_color_manual(values=c("black","red"))
